|

### 2021-11-04 submission/manuscript.rmd
create script for all rmse plots

For each patient we generated 8 baseline covariates here
$x_1,\dots,x_4\sim N(0, 1)$ and $x_5,\dots,x_8\sim B(1, 0.2)$. Treatment
was allocated using a 50:50 split. Outcomes for patients in the control arm were
generated from a logistic regression model including all baseline covariates. In
the base scenarios coefficient values were such, that the AUC of the
logistic regression model was $0.75$ and the event rate in the control arm was
$20\%$. Binary outcomes in the control arm were generated from Bernoulli variables
with true probabilities 
$P(y=1|X, t_x = 0) = \text{expit}(PI)=\frac{e^{PI}}{1+e^{PI}}$.

@@

$$\text{RMSE}=\frac{1}{n}\sum_{i=1}^n\big(\tau(\bm{x}_i) - \hat{\tau}(\bm{x}_i)\big)^2$$
We compared the discriminative ability of the methods under study using
c-for-benefit [@vanKlaveren2018]. The c-for-benefit represents the probability
that from two randomly chosen matched patient pairs with unequal observed
benefit, the pair with greater observed benefit also has a higher predicted
benefit. To be able to calculate observed benefit, patients in each treatment
arm are ranked based on their predicted benefit and then matched 1:1 across
treatment arms. *Observed* treatment benefit is defined as the difference of
observed outcomes between the untreated and the treated patient of each matched
patient pair. *Predicted* benefit is defined as the average of predicted benefit
within each matched patient pair.

>>>>

For each patient we generated 8 baseline covariates
$x_1,\dots,x_4\sim N(0, 1)$ and $x_5,\dots,x_8\sim B(1, 0.2)$. Treatment
was allocated using a 50:50 split. Outcomes for patients in the control arm were
generated from a logistic regression model including all baseline covariates. In
the base scenarios coefficient values were such, that the AUC of the
logistic regression model was $0.75$ and the event rate in the control arm was
$20\%$. Binary outcomes in the control arm were generated from Bernoulli variables
with true probabilities 
$P(y=1|X, t_x = 0) = \text{expit}(PI)=\frac{e^{PI}}{1+e^{PI}}$.

@@

$$\text{RMSE}=\sqrt{\frac{1}{n}\sum_{i=1}^n\big(\tau(\bm{x}_i) - \hat{\tau}(\bm{x}_i)\big)^2}$$
We compared the discriminative ability of the methods under study using
c-for-benefit [@vanKlaveren2018]. The c-for-benefit represents the probability
that from two randomly chosen matched patient pairs with unequal observed
benefit, the pair with greater observed benefit also has a higher predicted
benefit. To be able to calculate observed benefit, patients in each treatment
arm are ranked based on their predicted benefit and then matched 1:1 across
treatment arms. *Observed* treatment benefit is defined as the difference of
observed outcomes between the untreated and the treated patient of each matched
patient pair. *Predicted* benefit is defined as the average of predicted benefit
within each matched patient pair.
